The SMT Competition 2015--2018

### 2019-08-16 2018/report/SMT-COMP.tex
Affiliated with IJCAR in 2018

The competition is organized under the direction of the SMT Steering
Committee, which appoints the competition chair.  (This appointment
should happen ``within 30 days from the end of the current edition of
the SMT workshop''~\cite{smt-bylaws} but in practice has often
happened later.)  The competition chair then assembles a team of
organizers, and oversees the work for the next edition of the
competition.
%
The SMT Workshop includes a block of time to present the competitors
and results of the competition.  The workshop is affiliated with a
major conference in the field of automated reasoning each year: with
CAV in 2015, with IJCAR in 2016, again with CAV in 2017, and with FLoC
in~2018.  Consequently, its date varies.  Competition results were
presented on July~19 in 2015, on July~2 in 2016, on July~23 in 2017,
and on July~13 in~2018.

>>>>

The competition is organized under the direction of the SMT Steering
Committee, which appoints the competition chair.  (This appointment
should happen ``within 30 days from the end of the current edition of
the SMT workshop''~\cite{smt-bylaws} but in practice has often
happened later.)  The competition chair then assembles a team of
organizers, and oversees the work for the next edition of the
competition.
%
The SMT Workshop includes a block of time to present the competitors
and results of the competition.  The workshop is affiliated with a
major conference in the field of automated reasoning each year: with
CAV in 2015, with IJCAR in 2016, again with CAV in 2017, and with
IJCAR (as part of FLoC) in~2018.  Consequently, its date varies.
Competition results were presented on July~19 in 2015, on July~2 in
2016, on July~23 in 2017, and on July~13 in~2018.
